### 2021-03-19 ch/2-related-work.tex
Make a sentence slightly nicer

A perceived shortcoming of most methods in this area is that they rely on annotations for the subgroups.
Two papers that tried to circumvent this problem are \citet{HasSriNamLia18,nam2020learning},
both taking very different routes.
The first one tries to be robust with respect to all possible subgroups down to a certain size.
Essentially, the method tackles the worst-case scenario where the most egregiously misclassified samples form a subgroup.
The second approach is based on the idea that subgroups are easier to predict than the actual prediction targets.
After all, if this were not the case, then there would not really be a problem.
Thus, a classifier is learned in such a way that it predominantly tries to make ``easy'' predictions,
that is, samples where the model is very confident receive a higher weight.
The assumption is that this model learns to predict the subgroup (or spurious attribute),
for which no labels are available.
A second model is then trained, for which those samples are downweighted for which the first model was very confident;
the hope being that by learning the ``hard'' samples, the model learns the correct relationship.
Both \citet{HasSriNamLia18,nam2020learning} frame their methods as improving accuracy on an unbiased test set
and do not make references to fairness metrics,
but there is nevertheless a strong connection to the fairness literature.

>>>>

A perceived shortcoming of most methods in this area is that they rely on annotations for the subgroups.
Two papers that tried to circumvent this problem are \citet{HasSriNamLia18,nam2020learning},
both taking very different routes.
The first one tries to be robust with respect to all possible subgroups down to a certain size.
Essentially, the method tackles the worst-case scenario where the most egregiously misclassified samples form a subgroup.
The second approach is based on the idea that subgroups are easier to predict than the actual prediction targets.
After all, if this were not the case, then there would not really be a problem.
Thus, a classifier is learned in such a way that it predominantly tries to make ``easy'' predictions,
that is, samples where the model is very confident receive a higher weight.
The assumption is that this model learns to predict the subgroup (or spurious attribute),
for which no labels are available.
A second model is then trained, for which those samples are downweighted for which the first model was very confident;
the hope being that by learning the ``hard'' samples, the model learns the correct relationship.
Both \citet{HasSriNamLia18,nam2020learning} frame their methods as improving accuracy on an unbiased test set
and do not make references to fairness metrics,
but a strong connection to the fairness literature nevertheless exists.
